\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2025-05-09 scratch/JSS-submission/Final_submission/jss5535.tex
correct refs to /Figures dir in .tex file

{\centering \subfloat[\label{fig:mpg-horsepower-polynomials-1}]{\includegraphics[width=0.45\linewidth]{jss5535_files/figure-latex/mpg-horsepower-polynomials-1} }~~~\subfloat[\label{fig:mpg-horsepower-polynomials-2}]{\includegraphics[width=0.45\linewidth]{jss5535_files/figure-latex/mpg-horsepower-polynomials-2} }

@@

{\centering \subfloat[\label{fig:polynomial-regression-CV-graph-2-1}]{\includegraphics[width=0.5\linewidth]{jss5535_files/figure-latex/polynomial-regression-CV-graph-2-1} }~~~\subfloat[\label{fig:polynomial-regression-CV-graph-2-2}]{\includegraphics[width=0.5\linewidth]{jss5535_files/figure-latex/polynomial-regression-CV-graph-2-2} }

@@

{\centering \includegraphics[width=0.75\linewidth]{jss5535_files/figure-latex/plot1-1}

@@

{\centering \includegraphics[width=1\linewidth]{jss5535_files/figure-latex/plot-fits-combined-1}

@@

{\centering \includegraphics[width=0.75\linewidth]{jss5535_files/figure-latex/cross-validation-data-plot-1}

@@

{\centering \includegraphics[width=0.95\linewidth]{jss5535_files/figure-latex/Auto-explore-scatterplot-matrix-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{jss5535_files/figure-latex/Auto-explore-cr-plots-1}

@@

{\centering \includegraphics{jss5535_files/figure-latex/BEPS-plot-1}

>>>>

{\centering \subfloat[\label{fig:mpg-horsepower-polynomials-1}]{\includegraphics[width=0.45\linewidth]{Figures/mpg-horsepower-polynomials-1} }~~~\subfloat[\label{fig:mpg-horsepower-polynomials-2}]{\includegraphics[width=0.45\linewidth]{Figures/mpg-horsepower-polynomials-2} }

@@

{\centering \subfloat[\label{fig:polynomial-regression-CV-graph-2-1}]{\includegraphics[width=0.5\linewidth]{Figures/polynomial-regression-CV-graph-2-1} }~~~\subfloat[\label{fig:polynomial-regression-CV-graph-2-2}]{\includegraphics[width=0.5\linewidth]{Figures/polynomial-regression-CV-graph-2-2} }

@@

{\centering \includegraphics[width=0.75\linewidth]{Figures/plot1-1}

@@

{\centering \includegraphics[width=1\linewidth]{Figures/plot-fits-combined-1}

@@

{\centering \includegraphics[width=0.75\linewidth]{Figures/cross-validation-data-plot-1}

@@

{\centering \includegraphics[width=0.95\linewidth]{Figures/Auto-explore-scatterplot-matrix-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{Figures/Auto-explore-cr-plots-1}

@@

{\centering \includegraphics{Figures/BEPS-plot-1}
